Legends for supplementary material

### 2019-05-12 Manuscript/Figures/figure_legends.Rmd
fixed figure 8 (fig 15 in supp); averaged over all chrs; updated legends

**Figure 8. Predictive importance of genomic annotations for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878.** Importance was rescaled to values between 0 and 100, and discretized. The importance was subsequently sorted according to the most predictive annotations associated with the 10 kb resolution. Annotations with higher values of predictive importance are denoted in dark red, while annotations that were regularized in the pipeline for specific resolutions are denoted in grey.

@@

>>>>

@@

**Figure 8. Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878. Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100. Transcription factors with higher values of predictive importance are denoted in dark red.

### 2019-05-12 Manuscript/Supplementary/supplementary_legends.Rmd
fixed figure 8 (fig 15 in supp); averaged over all chrs; updated legends

**Supplementary Figure 15. Predictive importance of genomic annotations for random forest models implemented on SMOTE resampled data with distance-type predictors for K562.** Importance was rescaled to values between 0 and 100, and discretized. The importance was subsequently sorted according to the most predictive annotations associated with the 10 kb resolution. Annotations with higher values of predictive importance are denoted in dark red, while annotations that were regularized in the pipeline for specific resolutions are denoted in grey.

**Supplementary Figure 11.. Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple). Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types. The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.

>>>>

**Supplementary Figure 11. Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple). Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types. The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.

**Supplementary Figure 15. Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for K562. Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100. Transcription factors with higher values of predictive importance are denoted in dark red.
